Topological Sigma Models for Generalized Para-Complex Geometry

### 2020-01-05 newdraft.tex
please only add .tex files

\brian{geometry, change in gradings}
\david{how does the embedding of $SO(1,1)$ into $G_R$ reflect on the definition of $\QQ$?}

Let $(\eta,K_\pm,H=\rd b)$ be the bi-para-Hermitian geometry of the $(2,2)$ para-SUSY sigma model and let $\{Q^1_\pm,Q^1_\pm\}$ be the basis of the superalgebra \eqref{eq:(2,2)para}. We define the following nilpotent supercharge
\begin{align}\label{QQ_nilpotent}
\QQ=Q_L+Q_R,\quad Q_L=\frac{1}{2}(Q^1_++Q^2_+),\quad Q_R=\frac{1}{2}(Q^1_-+Q^2_-),
\end{align}
and we also introduce the usual notation 
\begin{align*}
\chi=\frac{1}{2}(\id+K_+)\psi_+=P_+\psi_+=\psi_+^{(1,0)_+},\quad\lambda=\frac{1}{2}(\id+K_-)\psi_-=P_-\psi_-=\psi_-^{(1,0)_-}.
\end{align*}
\btd{Where do $\chi$ and $\lambda$ live?}

>>>>

\david{how does the embedding of $SO(1,1)$ into $G_R$ reflect on the definition of $\QQ$?}
\brian{In Euclidean space, we choose an embedding $SO(2) \hookrightarrow G_R$. 
Then, the twisting supercharge is required to be invariant.
The obvious analog is to require an embedding $SO(1,1) \to G_R$ for which $\QQ$ is invariant.
This is the twisting homomorphism which tells us how to modify the Lorentz group.
}

\brian{
There is another piece of data we have to fix to get the $\mathbb{Z}$-grading in the twisted theory. 
Ordinarily this amounts to picking a homomorphism $U(1) \to G_R$ for which $\QQ$ is weight one. 
It appears no such twisting homomorphism is possible.
Indeed, every group homomorphism $U(1) \to SO(1,1) \times SO(1,1)$  are necessarily trivial since $U(1)$ is compact and $SO(1,1) \cong \RR \oplus \RR$ (the first copy is the connected component of the identity, and the second component is the connected component of minus identity).
This means we may have to slightly reimagine what ``twisting data" is here.
Since there is at least a copy of $\RR$ in $SO(1,1)$ we can probably use this to define a ``weight".}

Let $(\eta,K_\pm,H=\rd b)$ be the bi-para-Hermitian geometry of the $(2,2)$ para-SUSY sigma model and let $\{Q^1_\pm,Q^1_\pm\}$ be the basis of the superalgebra \eqref{eq:(2,2)para}. We define the following nilpotent supercharge
\begin{align}\label{QQ_nilpotent}
\QQ=Q_L+Q_R,\quad Q_L=\frac{1}{2}(Q^1_++Q^2_+),\quad Q_R=\frac{1}{2}(Q^1_-+Q^2_-),
\end{align}
\brian{Should we call this the  ``generalized para B twist"? It is invariant with respect to the anti-diagonal twisting homomorphism $SO(1,1) \to SO(1,1) \times SO(1,1)$. I think Kapustin-Li call this the axial.}
and we also introduce the usual notation 
\begin{align*}
\chi=\frac{1}{2}(\id+K_+)\psi_+=P_+\psi_+=\psi_+^{(1,0)_+},\quad\lambda=\frac{1}{2}(\id+K_-)\psi_-=P_-\psi_-=\psi_-^{(1,0)_-}.
\end{align*}
\btd{Where do $\chi$ and $\lambda$ live?}
